From DSL to HPC Component-Based Runtime:\\ A Multi-Stencil DSL Case Study

### 2015-07-30 WOLFHPC15/article/ms_msc.tex
section 4 fix helene 30_07

\paragraph{Creation of the dependency graph} From the synchronized ordered list of computations $\Gamma_{data}$, a dependency graph is built. A dependency exists between two computations (including synchronizations) if and only if a data read has been written by a previous computation in $\Gamma_{data}$, and if the computation domains intersect. In other words, the only case where a data dependency exists but is not taking into account is when the computation domains do not intersect. Nodes of the dependency graph represent computations of $\Gamma_{data}$, while edges are dependencies between them. The dependency graph $\Gamma_{hybrid}$ is a directed acyclic graph (\emph{dag}). For example, the dependency dag $\Gamma_{hybrid}$ of the example of Figure~\ref{fig:mslex} is illustrated in Figure~\ref{fig:hyb}.

@@

  \path[->]
    (c0) edge node {} (sy1)
    (sy1) edge node {} (c1)
    (c1)  edge node {} (c2)
          edge node {} (c3)
    (c2) edge node {} (sy4)
    (sy4) edge node {} (c4)
    (c4) edge node {} (c6)
    (c3) edge node {} (c5)
    (c5) edge node {} (c7)
    (c6) edge node {} (c7)
    (c7) edge node {} (sy8)
    (sy8) edge node {} (c8);
\end{tikzpicture}
\caption{$\Gamma_{hybrid}$ of Figure~\ref{fig:hyb}}
\label{fig:hyb}
\end{center}
\end{figure}

@@

  \path[->]
    (s0) edge node {} (c0)
         edge node {} (star1)
         edge node {} (c1)
         edge node {} (p0)
         edge node {} (c7)
         edge node {} (star8)
         edge node {} (c8)
    (p0) edge node {} (s1)
         edge node {} (s2)
    (s1) edge node {} (p1)
         edge node {} (c4)
         edge node {} (c6)
    (p1) edge node {} (c2)
         edge node {} (star4)
    (s2) edge node {} (c3)
         edge node {} (c5);
  \end{tikzpicture}
\caption{$\Gamma_{tsp}$ of Figure~\ref{fig:hyb}.}
\label{fig:tsp}
\end{center}
\end{figure}

>>>>

\paragraph{Creation of the dependency graph} From the synchronized ordered list of computations $\Gamma_{data}$, a dependency graph is built. A dependency exists between two computations (including synchronizations) if and only if a data read has been written by a previous computation in $\Gamma_{data}$, and if the computation domains intersect. In other words, the only case where a data dependency exists but is not taken into account is when the computation domains do not intersect. Nodes of the dependency graph represent computations of $\Gamma_{data}$, while edges are dependencies between them. The dependency graph $\Gamma_{hybrid}$ is a directed acyclic graph (\emph{dag}). For example, the dependency dag $\Gamma_{hybrid}$ of the example of Figure~\ref{fig:mslex} is illustrated in Figure~\ref{fig:hyb}.

@@

  \path[->]
    (c0) edge node {} (sy1)
    (sy1) edge node {} (c1)
    (c1)  edge node {} (c2)
          edge node {} (c3)
    (c2) edge node {} (sy4)
    (sy4) edge node {} (c4)
    (c4) edge node {} (c6)
    (c3) edge node {} (c5)
    (c5) edge node {} (c7)
    (c6) edge node {} (c7)
    (c7) edge node {} (sy8)
    (sy8) edge node {} (c8);
\end{tikzpicture}
\caption{$\Gamma_{hybrid}$ of the example of Figure~\ref{fig:mslex}}
\label{fig:hyb}
\end{center}
\end{figure}

@@

  \path[->]
    (s0) edge node {} (c0)
         edge node {} (star1)
         edge node {} (c1)
         edge node {} (p0)
         edge node {} (c7)
         edge node {} (star8)
         edge node {} (c8)
    (p0) edge node {} (s1)
         edge node {} (s2)
    (s1) edge node {} (p1)
         edge node {} (c4)
         edge node {} (c6)
    (p1) edge node {} (c2)
         edge node {} (star4)
    (s2) edge node {} (c3)
         edge node {} (c5);
  \end{tikzpicture}
\caption{$\Gamma_{tsp}$ of Figure~\ref{fig:hyb}. Nodes $S$ represent sequences, nodes $P$ represent parallel sections.}
\label{fig:tsp}
\end{center}
\end{figure}
